---
title: "Lab 01 - Hello R"
author: "Enhui Wang"
date: "2024/01/15"
output: 
  html_document: 
    fig_height: 4
    fig_width: 9
---

## Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
library(datasauRus)
```

## Exercises

### Exercise 1

The dataset has 1846 rows and 3 columns. It includes variabels 'dateset','x',and 'y'.

### Exercise 2

The answers for this exercise are already provided to help guide you. Clean up the narrative to reflect what you want to submit. Let’s break it into steps:

First, let's plot the data in the dino dataset:

```{r plot-dino, fig.height=3, fig.width=6}
dino_data <- datasaurus_dozen %>%
  filter(dataset == "dino")

ggplot(data = dino_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

Next, let's calculate the correlation between `x` and `y` in this dataset:

```{r cor-dino}
dino_data %>%
  summarize(r = cor(x, y))
```
The corrleation coefficent between x and y is r=-0.064, meaning that there is no linear relationship between the x and y variables in the 'dino' dataset. 


### Exercise 3

This is your turn to write the code and narrative for the star dataset. Follow the same steps as above to complete the analysis. Don't forget to label your chunks appropriately!

Note that the R chunks are labeled with `plot-star` and `cor-star` to provide spaces to place the code for plotting and calculating the correlation coefficient.
To finish, clean up the narrative by removing these instructions.

```{r plot-dino, fig.height=3, fig.width=6}
star_data <- datasaurus_dozen %>%
  filter(dataset == "star")

ggplot(data = star_data, mapping = aes(x = x, y = y)) +
  geom_point() 


```

I'm some filler text, you should replace me with more meaningful text...

```{r cor-star}
# Calculate the correlation coefficient for the "star" dataset
star_data %>%
  summarize(r = cor(x, y))

```
The corrleation coefficent between x and y is r=-0.0629, meaning that there is no linear relationship between the x and y variables in the 'star' dataset. The r for star is almost identical as the r for dino, indicating the star dataset does not have a stronger linear relationship.


### Exercise 4

```{r plot-dino, fig.height=3, fig.width=6}
circle_data <- datasaurus_dozen %>%
  filter(dataset == "circle")

ggplot(data = circle_data, mapping = aes(x = x, y = y)) +
  geom_point() 
```

```{r}
circle_data %>%
  summarize(r = cor(x, y))

```
The corrleation coefficent between x and y is r=-0.06834336	, meaning that there is no linear relationship between the x and y variables in the 'circle' dataset. The r for circle is almost identical as the r for dino, indicating the star dataset does not have a stronger linear relationship.

### Exercise 5
```{r}
ggplot(datasaurus_dozen, aes(x = x, y = y, color = dataset)) +
  geom_point() +
  facet_wrap(~dataset, ncol = 3) +
  theme(legend.position = "none")
  
```{r}
  datasaurus_dozen %>%
  group_by(dataset) %>%
  summarize(r = cor(x, y)) %>%
  print(13)


